### 2015-02-16 Publications/2015-NeuroImage/03-introduction.tex
Change to Neuroimage layout

\IEEEPARstart{N}{onlinear} registration of images is a challenging task ubiquitous
  in an endless number of image analysis applications.
The problem is solved finding a spatial mapping $U$ that aligns the
  information given in two different coordinate systems (generally called
  \emph{reference}, $R$, and \emph{moving}, $M$):
  \begin{align}
  U\colon R \subset \mathbb{R}^n &\to M \subset \mathbb{R}^n \notag\\
  \vec{r} &\mapsto \vec{r}' =\vec{r}+u(\vec{r}),
  \label{eq:transform}
  \end{align}
  where $\vec{r}$ denotes a position in the reference domain and $\vec{r}'$
  its corresponding location in the target, and $n$ the dimension of domains
  ($n=3$ for 3D images).
Finally, $\vec{u} = u(\vec{r})$ is the function that models the displacement
  of every point in the reference domain.

The wide range of applications has derived in an intensive generation of diverse
  registration methods.
In a recent and comprehensive survey by \citeauthor{sotiras_deformable_2013}
  \citep{sotiras_deformable_2013}, registration methods are classified by
  matching criteria, deformation model, and optimization method.
The most widespread matching criteria are probably the so-called \emph{iconic
  methods} in \citep{sotiras_deformable_2013}.
However they are not appropriate for all the registration problems
  \citep{greve_accurate_2009}.
They propose a \emph{hybrid method} \citep{sotiras_deformable_2013} for the
  intra-subject registration of \gls*{t1} \gls*{mri} and \gls*{dmri} images
  of the brain using a linear transformation model.
As in \citep{greve_accurate_2009}, we exploit the precise structures that
  can be readily extracted with widely-used tools at high resolution
  and map this prior information to low resolution data,
  in which the scale of the imaged structures is in the range of the image
  resolution or above.
Our approach differs with \citep{greve_accurate_2009} in two fundamental
  choices: 1) We use a nonlinear deformation model that enables the
  correction of the susceptibility-derived distortions
  \citep{jezzard_correction_1995} that \gls*{dmri} data typically present.
And 2) our matching criteria does not necessarily need for clear intensity
  steps at the tissue interfaces where surfaces must be fitted.

\subsection{Related work}
\label{sec:methods_background}
Registration-segmentation methods are typically built including a deformation
  model to guide the evolution of a segmentation algorithm.
Even though some Bayesian approaches have been proposed to solve the joint problem
  \citep{wyatt_map_2003}, segmentation is usually performed using an evolving
  active contour \citep{chan_active_2001} that normally includes a shape prior
  term to the energy functional \citep{chen_using_2002,bresson_variational_2006,
  chan_level_2005,cremers_kernel_2006,gastaud_combining_2004}.
These methods generally have an explicit description of the expected relative boundary
  locations of the object to be delineated, and some, even model the statistical deviations
  from this average shape.

An early ``morphing''-segmentation approach was proposed in \citep{bertalmio_morphing_2000},
  and the first proper registration method was presented by \citeauthor{yezzi_variational_2001}
  \citep{yezzi_variational_2001}, where the energy functional is defined simultaneously in the target
  and reference images with an affine transformation supporting the coordinates mapping
  (the so-called ``2 \glspl*{pde} approach'').
\citeauthor{vemuri_joint_2003} proposed the first atlas-based registration \citep{vemuri_joint_2003}
  based on the level-sets framework and using only one \gls*{pde}.
The principal application of these techniques was the image registration between timesteps in
  a time-series or between different images \citep{paragios_level_2003}.
\citeauthor{unal_coupled_2005} \citep{unal_coupled_2005} extended the idea of
  \citep{bertalmio_morphing_2000,yezzi_variational_2001} to nonlinear registration
  using a free deformation field model.
A summary of these second set of techniques is performed in \citep{droske_mumfordshah_2009},
  proposing two different approaches to applying the Mumford-Shah \citep{mumford_optimal_1989}
  functional in joint registration and segmentation, through the propagation of the deformation
  field from the contours to the whole image definition.
Finally, \citeauthor{gorthi_active_2011} presented a comprehensive generalization of the
  existing methodologies \citep{gorthi_active_2011} based on the level-sets approximation.
Even though the historical evolution of joint segmentation and registration procedures is strongly
  linked to the level sets approximation, our work is based in derivations of the \acrlong{acwe}
  framework \citep{chan_active_2001}, and related to \citep{guyader_combined_2011}.

Finally, a derivation of the latter group is composed by atlas-based segmentation methods
  \citep{gorthi_segmentation_2009,gorthi_active_2011,pohl_unifying_2005,pohl_bayesian_2006,
  wang_joint_2006}, where the prior imposes consistent voxel-based classification of contiguous
  regions.
A comprehensive summary of the methodologies derived from the \gls{acwe} model, with special attention
  to joint registration-segmentation methods is found in \citep{gorthi_active_2011}.

@@

\subsection{Susceptibility-derived distortions}

\subsection{Our framework}
\label{sec:our_framework}

>>>>

\IEEEPARstart{N}{onlinear} registration of images is a challenging task ubiquitous
  in an endless number of image analysis applications.
The process aims to find a spatial mapping $U$ that aligns the information available
  in two different coordinate systems (generally called
  \emph{reference}, $R$, and \emph{moving}, $M$):
  \begin{align}
  U\colon R \subset \mathbb{R}^n &\to M \subset \mathbb{R}^n \notag\\
  \vec{r} &\mapsto \vec{r}' =\vec{r}+u(\vec{r}),
  \label{eq:transform}
  \end{align}
  where $\vec{r}$ denotes a position in the reference domain $R$, $\vec{r}'$ is
  its corresponding location in $M$, and $n$ the dimensionality of images.
Finally, $\vec{u} = u(\vec{r})$ is the displacement of every point with respect
  to the reference domain.
A comprehensive survey by \citeauthor{sotiras_deformable_2013} \citep{sotiras_deformable_2013}
  illustrates the wide variety of existing registration methodologies.
They classify the algorithms by the three principal building blocks that can be identified
  among methods: the matching criteria or similarity function to evaluate the proximity of
  the solution, the deformation model that may implement theoretical properties and constraints
  of the mapping in the selected application, and the optimization method or search strategy.
The most widespread matching criteria are probably the so-called \emph{iconic
  methods} \citep{sotiras_deformable_2013}.
These algorithms require the definition of an appropriate function on the voxel-wise information
  content of both images.
A second group, called \emph{geometric methods}, measure distances between features derived from
  corresponding objects defined in both spaces, such as landmarks, shapes, surfaces, etc.
Finally, \emph{hybrid methods} combine properties of the iconic and geometric methods.
As reviewed in \citep{sotiras_deformable_2013}, an important research effort has been devoted to
  study application-oriented matching criteria.

Currently uprising applications, such as the extraction of connectivity networks from
  diffusion \gls*{mri} \citep{craddock_imaging_2013}, demand for improved approaches
  that outperform existing techniques.
We propose the image registration -based solution to correct for the
  susceptibility distortions in \gls*{dmri} of the brain ,
  that is involved in the extraction of the structural connectivity map of the brain.
However they are not appropriate for all the registration problems
  \citep{greve_accurate_2009}.
They propose a \emph{hybrid method} \citep{sotiras_deformable_2013} for the
  intra-subject registration of \gls*{t1} \gls*{mri} and \gls*{dmri} images
  of the brain using a linear transformation model.
As in \citep{greve_accurate_2009}, we exploit the precise structures that
  can be readily extracted with widely-used tools at high resolution
  and map this prior information to low resolution data,
  in which the scale of the imaged structures is in the range of the image
  resolution or above.
Our approach differs with \citep{greve_accurate_2009} in two fundamental
  choices: 1) We use a nonlinear deformation model that enables the
  correction of the susceptibility-derived distortions
  \citep{jezzard_correction_1995} that \gls*{dmri} data typically present.
And 2) our matching criteria does not necessarily need for clear intensity
  steps at the tissue interfaces where surfaces must be fitted.

The hypothesis underpinning this research is that, in those situations,
  image registration can be reliably performed by searching for homogeneous
  regions in one image corresponding to a prior knowledge of the shape of objects in
  the moving coordinate system.

@@

### 2015-02-16 Publications/2015-NeuroImage/04-methods.tex
Change to Neuroimage layout

% -*- root: 00-main.tex -*-
\section{Methods}
\label{sec:methods}
%

>>>>

% -*- root: 00-main.tex -*-
\section{Methods}
\label{sec:methods}
%
\subsection{Related work}
\label{sec:methods_background}
Registration-segmentation methods are typically built including a deformation
  model to guide the evolution of a segmentation algorithm.
Even though some Bayesian approaches have been proposed to solve the joint problem
  \citep{wyatt_map_2003}, segmentation is usually performed using an evolving
  active contour \citep{chan_active_2001} that normally includes a shape prior
  term to the energy functional \citep{chen_using_2002,bresson_variational_2006,
  chan_level_2005,cremers_kernel_2006,gastaud_combining_2004}.
These methods generally have an explicit description of the expected relative boundary
  locations of the object to be delineated, and some, even model the statistical deviations
  from this average shape.

An early ``morphing''-segmentation approach was proposed in \citep{bertalmio_morphing_2000},
  and the first proper registration method was presented by \citeauthor{yezzi_variational_2001}
  \citep{yezzi_variational_2001}, where the energy functional is defined simultaneously in the target
  and reference images with an affine transformation supporting the coordinates mapping
  (the so-called ``2 \glspl*{pde} approach'').
\citeauthor{vemuri_joint_2003} proposed the first atlas-based registration \citep{vemuri_joint_2003}
  based on the level-sets framework and using only one \gls*{pde}.
The principal application of these techniques was the image registration between timesteps in
  a time-series or between different images \citep{paragios_level_2003}.
\citeauthor{unal_coupled_2005} \citep{unal_coupled_2005} extended the idea of
  \citep{bertalmio_morphing_2000,yezzi_variational_2001} to nonlinear registration
  using a free deformation field model.
A summary of these second set of techniques is performed in \citep{droske_mumfordshah_2009},
  proposing two different approaches to applying the Mumford-Shah \citep{mumford_optimal_1989}
  functional in joint registration and segmentation, through the propagation of the deformation
  field from the contours to the whole image definition.
Finally, \citeauthor{gorthi_active_2011} presented a comprehensive generalization of the
  existing methodologies \citep{gorthi_active_2011} based on the level-sets approximation.
Even though the historical evolution of joint segmentation and registration procedures is strongly
  linked to the level sets approximation, our work is based in derivations of the \acrlong{acwe}
  framework \citep{chan_active_2001}, and related to \citep{guyader_combined_2011}.

Finally, a derivation of the latter group is composed by atlas-based segmentation methods
  \citep{gorthi_segmentation_2009,gorthi_active_2011,pohl_unifying_2005,pohl_bayesian_2006,
  wang_joint_2006}, where the prior imposes consistent voxel-based classification of contiguous
  regions.
A comprehensive summary of the methodologies derived from the \acrlong{acwe} model, with special attention
  to joint registration-segmentation methods is found in \citep{gorthi_active_2011}.
